Distributional Trees for Circular Data

### 2019-02-07 pkg/disttree/inst/IWSM2019/abstract_IWSM2019_schlosser.tex
Update affilitation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2452 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 87344947a7c4c486c38d7a84bb2b527b2fe3fd4a

%%%%%%%% IF DEPARTMENTS ARE LISTED AS WELL CHANGE NUMBERING!!!  %%%%%%%%%%%%%%
\institute{Department of Statistics, Universit\"at Innsbruck, Innsbruck, Austria
\and Department of Atmospheric and Cryospheric Science, Universit\"at Innsbruck, Innsbruck, Austria
\and Epidemiology, Biostatistics and Prevention Institute, Universit\"at Z\"urich, Zurich, Switzerland}

>>>>

%%%%%%%% IF DEPARTMENTS ARE LISTED AS WELL CHANGE NUMBERING!!!  %%%%%%%%%%%%%%
\institute{Department of Statistics, University of Innsbruck, Innsbruck, Austria
\and Department of Atmospheric and Cryospheric Science, University of Innsbruck, Innsbruck, Austria
\and Epidemiology, Biostatistics and Prevention Institute, University of Zurich, Zurich, Switzerland}
